First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
Implement Stepan iremark and clean latex syntax

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading-order, twist-2, handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section of coherent scattering is suppressed due to the nuclear form factor, and second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
%The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
%to measure due to its small cross section and the necessity to ensure 
%exclusivity of the reaction, i.e. the target nucleus.
Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

@@

%The main challenge in studying nuclear DVCS is ensuring the exclusivity of the reaction. 
Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

%The main background in the measurement of DVCS is coherent $\pi^{0}$ 
%production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
%invariant mass reconstruction of two photons.

@@

%most of uncertainties of the 
%experimental normalization and in detector efficiencies will cancel out.

The DVCS reaction is experimentally indistinguishable from the well-known 
Bethe-Heitler (BH) process, where the final photon is emitted either from the 
incoming or the outgoing leptons. At leading twist and leading order, the 
deeply virtual photon production cross section is composed of BH, DVCS, and 
interference terms. While the BH is not sensitive to GPDs and does not carry 
information about the partonic structure of the hadronic target, its 
interference with the DVCS reaction is sensitive to GPDs enhancing the DVCS 
small cross section at the kinematical regions explored at Jefferson Lab. The 
amplitudes of the three terms can be approximated as a finite sum of Fourier 
harmonics, as shown for the nucleon in \cite{Belitsky:2001ns} and for the 
spin-zero targets in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these 
approximations, the beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can 
then be expressed as:
\small
\begin{equation}
\begin{split}
A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
 \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\label{eq:A_LU-coh}
\end{split}
\end{equation}
\normalsize
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi),\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} 
   \cos(2\phi),\\ \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
C_{++}(0) +  C_{++}(1) cos(\phi) \right),\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2},
\end{eqnarray}
\normalsize
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

>>>>

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence. 
Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

@@

Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

@@

The DVCS and the well-known Bethe-Heitler (BH) process, where the final real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of the real photon 
electroproduction is a sum of amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, where the DVCS amplitude is 
a combination of the form factors and GPDs. In our kinematics, the cross 
section of the real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering in the cross section calculation, 
BH and DVCS amplitude squared, and the interference of the BH and DVCS amplitudes 
can be expressed by a finite sum of Fourier harmonics, as shown for the nucleon 
in \cite{Belitsky:2001ns} and for the spin-zero targets in 
\cite{Kirchner:2003wt,Belitsky:2008bz}. Base on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.
